Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

# Create Random Forest Model
set.seed(123)
# Create Random Forest Model
# Use grid of tuning parameters
model4 <- rand_forest(mtry = tune("mtry"),
                     min_n = tune("min_n")) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")
# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)

@@

res %>% 
    collect_metrics()

>>>>

```{r Random Forest}
# Create Random Forest Model
set.seed(123)
# Use grid of tuning parameters
model4 <- rand_forest(mtry = tune("mtry"),
                     min_n = tune("min_n")) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")
# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)

@@

res %>% 
    collect_metrics()
```
